Rapid and Accurate Global PTM Discovery (G-PTM-D) Using Post-Acquisition Spectral Calibration and Multi-Notch Searches

### 2017-07-10 paper.tex
dfjakdf

\title[Rapid and Accurate Global PTM Discovery (G-PTM-D) Using Post-Acquisition Spectral Calibration and Defined Mass Windows]
  {Rapid and Accurate Global PTM Discovery (G-PTM-D) Using Post-Acquisition Spectral Calibration and Defined Mass Windows}

@@

The idea of restricting the search space by only allowing certain mass differences between the precursor and the identified peptide mass is useful in procedures beyond the G-PTM-D workflow.
Its efficacy is demonstrated in context of a search for novel modifications, which is usually based on unrestricted searches.
A combination of specialized notch and interval searches produces superior identification and discovery results.

>>>>

\title[Rapid and Accurate Global PTM Discovery (G-PTM-D) Using Post-Acquisition Spectral Calibration and Multi-Notch Searches]
  {Rapid and Accurate Global PTM Discovery (G-PTM-D) Using Post-Acquisition Spectral Calibration and Multi-Notch Searches}

@@
